Reasoning About a Machine with Local Capabilities

### 2019-07-04 toplas/paper.tex
[TOPLAS] Disable toplas command and environment
Update my affiliation.
[TOPLAS] Update malloc specification

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}%{}{}
    {\color{OliveGreen}}{}
\newenvironment{toplassug}
    {\begin{comment}}{\end{comment}}

\newcommand{\itoplas}[1]%{#1}
    {{\color{OliveGreen} #1}}
\newcommand{\itoplassug}[1]{}
%    {{\color{Blue} #1}}

@@

\author{Dominique~Devriese}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{iMinds-DistriNet}              %% \department is recommended
  \institution{KU Leuven}            %% \institution is required
  \streetaddress{Celestijnenlaan 200 A}
  \city{Leuven}
  \postcode{3001}
  \country{Belgium}
}
\email{dominique.devriese@cs.kuleuven.be}          %% \email is recommended

\author{Lars~Birkedal}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{Aarhus University}            %% \institution is required
  \streetaddress{\AA{}bogade 34}
  \city{Aarhus}
  \postcode{8210}
  \country{Denmark}
}
\email{birkedal@cs.au.dk}          %% \email is recommended
% \author{Lau~Skorstengaard\inst{1} \and Dominique~Devriese\inst{2} \and Lars~Birkedal\inst{1}}
% \institute{Aarhus University \\ \email{\{lau,birkedal\}@cs.au.dk}
% \and imec-DistriNet, KU Leuven \\ \email{dominique.devriese@cs.kuleuven.be}}

@@

\begin{definition}[Malloc Specification]
  \label{spec:malloc}
  $c_\malloc$ satisfies the specification for malloc iff the following
  conditions hold:
  \begin{enumerate}
  \item \label{item:malloc-spec:eg} $c_\malloc = ((\entry,\glob),\_,\_,\_)$
  \item \label{item:malloc-spec:reg} There exists a $\iota_{\malloc,0}$ such that
    \begin{enumerate}
    \item \label{item:malloc-spec:perm} $\iota_{\malloc,0}.v = \perma$
    \item \label{item:malloc-spec:independent} For all $\iota' \futurestr \iota_{\malloc,0}, W,i$ with
      $W(i)=\iota'$, we have that
      \begin{equation*}
        \iota'.H (\iota'.s) (\xi^{-1}(W)) = \iota'.H (\iota'.s) (\xi^{-1}([i \mapsto W(i)]))
      \end{equation*}
    \item \label{item:malloc-spec:correct-exec} For all $\Phi \in \ExecConfs$, $\ms_{\var{footprint}}, \hsframe \in
      \HeapSegments$, $i, n, \size \in \nats$, $w_{\var{ret}} \in \Words$,
      $\iota_\malloc \futurestr \iota_{\malloc,0}$, we have that
      \[
        \begin{array}{l}
          \text{If }
          \memheap = \ms_{\var{footprint}} \uplus \hsframe \land \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land{} \\
          \quad\memreg(r_1) = \size \land \size \geq 0 \land  \memreg(r_0) = w_{\var{ret}} \land{} \\
          \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
          \text{Then, } \\
          \quad \exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
          \qquad \exists j \in \nats \ldotp j > 0 \land \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
          \qquad \quad \Phi \step[j] \Phi' \land{} \\
          \qquad \quad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land{}\\
          \qquad \quad \iota_{\malloc}' \futurewk \iota_\malloc \land{} \\
          \qquad \quad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land{} \\
          \qquad \quad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land{} \\
          \qquad \quad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')} \land{} \\
          \qquad \quad \size - 1 = e'-b'
        \end{array}
      \]
    \item \label{item:malloc-spec:fail} For all $\Phi \in \ExecConfs$,
      \[
        \begin{array}{l}
          \text{If } (\memreg(r_1) \notin \ints \vee \memreg(r_1) < 0) \land
          \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\
          \text{Then } \exists j \in \nats \ldotp \Phi \step[j] \failed
        \end{array}
      \]
    \end{enumerate}
  \end{enumerate}
\end{definition}

@@

For convenience, we also require that malloc returns the non-argument registers
of the register-file unchanged after the call. This allows the caller to keep
private capabilities in the register file, without having to protect them by
storing them in a private stack frame.

>>>>

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}{}{}
%    {\color{OliveGreen}}{}
\newenvironment{toplassug}
    {\begin{comment}}{\end{comment}}

\newcommand{\itoplas}[1]{#1}
%    {{\color{OliveGreen} #1}}
\newcommand{\itoplassug}[1]{}
%    {{\color{Blue} #1}}

@@

\author{Dominique~Devriese}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Vakgroep Computerwetenschappen}              %% \department is recommended
  \institution{Vrije Universiteit Brussel}            %% \institution is required
  \streetaddress{Pleinlaan 2}
  \city{Elsene}
  \postcode{1050}
  \country{Belgium}
}
\email{dominique.devriese@vub.be}          %% \email is recommended

\author{Lars~Birkedal}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{Aarhus University}            %% \institution is required
  \streetaddress{\AA{}bogade 34}
  \city{Aarhus}
  \postcode{8210}
  \country{Denmark}
}
\email{birkedal@cs.au.dk}          %% \email is recommended
% \author{Lau~Skorstengaard\inst{1} \and Dominique~Devriese\inst{2} \and Lars~Birkedal\inst{1}}
% \institute{Aarhus University \\ \email{\{lau,birkedal\}@cs.au.dk}
% \and Vrije Universiteit Brussel \\ \email{dominique.devriese@vub.be}}

@@

\begin{definition}[Malloc Specification]
  \label{spec:malloc}
  $c_\malloc$ satisfies the specification for malloc iff the following
  conditions hold:
  \begin{enumerate}
  \item \label{item:malloc-spec:eg} $c_\malloc = ((\entry,\glob),\_,\_,\_)$
  \item \label{item:malloc-spec:reg} There exists a $\iota_{\malloc,0}$ such that
    \begin{enumerate}
    \item \label{item:malloc-spec:perm} $\iota_{\malloc,0}.v = \perma$
    \item \label{item:malloc-spec:independent} For all $\iota' \futurestr \iota_{\malloc,0}, W,i$ with
      $W(i)=\iota'$, we have that
      \begin{equation*}
        \iota'.H (\iota'.s) (\xi^{-1}(W)) = \iota'.H (\iota'.s) (\xi^{-1}([i \mapsto W(i)]))
      \end{equation*}
    \item \label{item:malloc-spec:correct-exec} For all $\Phi \in \ExecConfs$, $\ms_{\var{footprint}}, \hsframe \in
      \HeapSegments$, $i, n, \size \in \nats$, $w_{\var{ret}} \in \Words$,
      $\iota_\malloc \futurestr \iota_{\malloc,0}$, we have that
      \[
        \begin{array}{l}
          \text{If }
          \memheap = \ms_{\var{footprint}} \uplus \hsframe \land \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land{} \\
          \quad\memreg(r_1) = \size \land \size \geq 0 \land  \memreg(r_0) = w_{\var{ret}} \land{} \\
          \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
          \text{Then, } \\
          \quad \exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
          \qquad \exists j \in \nats \ldotp j > 0 \land \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
          \qquad \quad \Phi \step[j] \Phi' \land{} \\
          \qquad \quad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land{}\\
          \qquad \quad \iota_{\malloc}' \futurewk \iota_\malloc \land{} \\
          \qquad \quad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land{} \\
          \qquad \quad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land{} \\
          \qquad \quad \memreg[\Phi'] = \memreg[\Phi]\arraycolsep=0pt\array[t]{l}\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\\\update{r_1}{((\rwx,\glob),b',e',b')}\\\update{r_\var{t1},r_\var{t2},r_\var{t3}}{0,0,0} \land{}\endarray  \\
          \qquad \quad \size - 1 = e'-b'
        \end{array}
      \]
    \item \label{item:malloc-spec:fail} For all $\Phi \in \ExecConfs$,
      \[
        \begin{array}{l}
          \text{If } (\memreg(r_1) \notin \ints \vee \memreg(r_1) < 0) \land
          \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\
          \text{Then } \exists j \in \nats \ldotp \Phi \step[j] \failed
        \end{array}
      \]
    \end{enumerate}
  \end{enumerate}
\end{definition}

@@

For convenience, we also require that malloc returns the non-argument registers (except registers for malloc internal computations) of the register-file unchanged after the call.
This allows the caller to keep private capabilities in the register file, without having to protect them by storing them in a private stack frame.
